Digital History in Finland, 1488-1828

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

TODO: why Fennica has huge drop in 1700s

@@

```{r selectedplaces2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="0px"}

>>>>

Why Fennica has huge drop in 1700s. Do some publisher disappear (TODO). Let us look at top publication places in Fennica:

```{r drop1700, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
selected.places = names(top(subset(df0, catalog == "Fennica"), "publication_place", 10))
for (myplace in selected.places) {
  # Use timeinterval year intervals
  catal = "Fennica"
  minyear = 1650
  maxyear = 1750

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot(data = dfm, aes(x = date, y = Documents))
  p <- p + geom_line(col = "black")
  #p <- p + geom_smooth(col = "black")  
  p <- p + geom_point(col = "black", size = 3)
  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20), limits = c(minyear, maxyear))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))

  print(p)
}
```

@@

```{r selectedplaces2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="600px"}
